Detecting Photo Manipulation using Reflections on Curved Surfaces

### 2014-02-03 paper/main.tex
fixed mode selection UI bug, added plain sphere tests
created diagrams for paper, added images with true center displayed
some work on cluster finding and testing with altered images

\begin{figure}
	\centering
    	\includegraphics[width=0.8\textwidth]{planar-vanishing-point-forged}
	\caption{Demonstration of vanishing point inconsistency. The lines corresponding to the man on the left converge to a different vanishing point than those from the rest of the scene, so it is likely that the man and his reflection were edited into the scene. \cite{obrien12}}
	\label{planar-vanishing-point-forged}
\end{figure}

\begin{figure}
	\centering
    	\includegraphics[width=0.8\textwidth]{planar-midpoint-genuine}
	\caption{Demonstration of midpoint and vanishing point consistency. The lines converge to a well-defined vanishing point $V$. Additionally, the midpoints in three-dimensional scene space between the real and reflected features plausibly intersect the mirror plane. \cite{obrien12}}
	\label{planar-midpoint-genuine}
\end{figure}

\begin{figure}
	\centering
    	\includegraphics[width=0.8\textwidth]{center-of-projection-planar-genuine}
	\caption{Demonstration of center of projection consistency. The pink and blue point clouds represent sets of possible solutions, generated by randomly perturbing the points selected that form the lines. Since the point clouds intersect, there is a possible consistent center of projection, or camera position. \cite{obrien12}}
	\label{center-of-projection-planar-genuine}
\end{figure}

@@

\subsection{Properties of Reflective Geometry}
% Will contain some more technical references to O'Brien/Farid paper where needed
Reflection of light on a surface is entirely dependent on the surface normal in a straightforward relation. The incident ray (or ray of light coming towards the surface) must make the same angle with the normal as the reflected ray.  Additionally, the incident ray, reflected ray, and normal must all be coplanar, and the reflected and incident rays must be on opposite sides of the normal.

\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{normal-reflection}
	\caption{Given a camera location $C$, a point $P$ on an object and its corresponding reflection $R$, the ray $PR$ appears equivalent to the ray $PB$ from the point of view of the camera. The ray $PR$ is also perpendicular to the surface normal $N$. Since all of the points in this diagram must be coplanar, this holds true in 3D space. \cite{obrien12}}
	\label{normal-reflection}
\end{figure}

@@

In the case of a curved surface, the ray is still parallel to the normal at the point of reflection. However, all such rays through the same mirror will not be parallel in three-dimensional space because the normal is not constant.
% relationship between normal and reflection angle
% colinearity of 3-D line between real and virtual object, and line between real object and reflection - why planar works
% still parallel to normal even if surface is curved

% TODO actual techniques

@@

\section{Conclusion}
\subsection{Results}
\subsection{Future Work}

>>>>

\begin{figure}
	\centering
    	\includegraphics[width=0.8\textwidth]{planar-vanishing-point-forged}
	\caption{Demonstration of vanishing point inconsistency. The lines corresponding to the man on the left converge to a different vanishing point than those from the rest of the scene, so it is likely that the man and his reflection were edited into the scene. \cite[Fig.~1]{obrien12}}
	\label{planar-vanishing-point-forged}
\end{figure}

\begin{figure}
	\centering
    	\includegraphics[width=0.8\textwidth]{planar-midpoint-genuine}
	\caption{Demonstration of midpoint and vanishing point consistency. The lines converge to a well-defined vanishing point $V$. Additionally, the midpoints in three-dimensional scene space between the real and reflected features plausibly intersect the mirror plane. \cite[Fig.~3]{obrien12}}
	\label{planar-midpoint-genuine}
\end{figure}

\begin{figure}
	\centering
    	\includegraphics[width=0.8\textwidth]{center-of-projection-planar-genuine}
	\caption{Demonstration of center of projection consistency. The pink and blue point clouds represent sets of possible solutions, generated by randomly perturbing the points selected that form the lines. Since the point clouds intersect, there is a possible consistent center of projection, or camera position. \cite[Fig.~6]{obrien12}}
	\label{center-of-projection-planar-genuine}
\end{figure}

@@

\subsection{Properties of Reflective Geometry}
% Will contain some more technical references to O'Brien/Farid paper where needed
Reflection of light on a surface is directly related to the surface normal at the point of reflection. The incident ray (or ray of light coming towards the surface) must make the same angle with the normal as the reflected ray.  Additionally, the incident ray, reflected ray, and normal must all be coplanar, and the reflected and incident rays must be on opposite sides of the normal.

\begin{figure}
	\centering
    	\includegraphics[width=0.6\textwidth]{normal-reflection}
	\caption{Given a camera location $C$, a point $P$ on an object and its corresponding reflection $R$, the ray $PR$ appears equivalent to the ray $PB$ from the point of view of the camera. The ray $PR$ is also perpendicular to the surface normal $N$. Since all of the points in this diagram must be coplanar, this holds true in 3D space. \cite[Fig.~2]{obrien12}}
	\label{normal-reflection}
\end{figure}

@@

In the case of a curved surface, the ray is still parallel to the normal at the point of reflection. However, all such rays through the same mirror will not be parallel in three-dimensional space because the normal is not constant.

\subsection{Reflective Sphere Geometry}
% figure: colinearity of radius and projection of incident ray

@@

The application consists of a Python script that uses PySide for GUI and drawing, and numpy/scipy for mathematical calculations.

\subsection{Circle Finding}
\subsection{Edge Detection}
rudimentary edge detection to assist picking points for the circles
limitation: edges are relatively easy to find in these test images- plain background

\subsection{Distortion from Perspective Projection}
% move to mathematical techniques section?

\section{Conclusion}
\subsection{Results}
\subsubsection{Effects of Human Error}
\subsection{Future Work}
